---
title: "Regex.rmd"
author: "Alycea Wood"
date: "1/28/2020"
output: html_document
---

```{r loading libraries, echo=T, include = F}
library(dplyr)
library(stringr)
```


So the first step we are going to do is import our "measurements" dataset.

```{r loading in dataset, echo=T}
MData = read.csv("Data/measurements.csv")
print(MData)
```

Now I'm going to add a new column named "Sp" that also changes the genus in species names to only the first letter and a period.

```{r adding "Sp" column, echo=T}
Sp1 = sub(" ",". ", MData$Species)
MData$Sp = sub("(\\w)\\w+","\\1", Sp1)
head(MData$Sp)
head(MData)
```

Now I am going to create a new dataframe where Sp replaces the Species column. I also decided to get rid of the "X" column because I was noticing it was there and I don't think it was supposed to be there in the first place (plus now the dataset looks a little cleaner!).

```{r sp replacing Species}
NoSpeciesMData = select(MData,-Species, -X)
NewMData = select(NoSpeciesMData, Sp, everything())
head(NewMData)
```

